The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-01-27 paper/sections/methods.tex
methods

@@

@@

Attempting to use $\Pmatxi$ in~\refeq{shapematch} on a per-part basis is problematic as it can become ill-posed, especially for planar boundary representations. 
To alleviate this problem we invoke the \emph{hierarchical ordering principle}, which argues that the behavior of a system is typically 
dominated by lower order effects~\cite{li2006regularities}. 
Mechanically, this principle suggests that the amount of motion modelled by increasingly high-order polynomials is decreasing. 
This implies that we can achieve acceptable shape matching results by performing shape matching hierarchically -- starting with the constant term and then 
fitting the remaining deformation with progressively higher-order deformations.

\begin{equation}
    \begin{split}
        \tr_i  & = \sum_{\prt_k \in \bar{\refX}_j} \underbrace{\mathbbm{1}^T\wt_k \samp{\Jnurbs}_k}_{B_{ik}}\vc{q}_k \\
        \vc{c}_i^1 & = \smash{\underbrace{\left(\samp{\Pmat^1}^T\wt_i\samp{\Pmat^1}\right)}_{A^1_i}}^{-1}\bigg(\underbrace{\samp{\Pmat^1}^T\wt_i\samp{\Jnurbs}_i}_{B^1_i}\vc{q}_i-\underbrace{\samp{\Pmat^1}^T\wt_i\mathbbm{1}}_{T^1_i}\tr_i\bigg)\\
        \vc{c}_i^2 & = \smash{\underbrace{\left(\samp{\Pmat^2}^T\wt_i\samp{\Pmat^2}\right)}_{A^2_i}}^{-1}\bigg(\underbrace{\samp{\Pmat^2}^T\wt_i\samp{\Jnurbs}_i}_{B^2_i}\vc{q}_i-\underbrace{\samp{\Pmat^2}^T\wt_i\samp{\Pmat^1}}_{D^2_i}\vc{c}_i^1 - \underbrace{\samp{\Pmat^2}^T\wt_i\mathbbm{1}}_{T^2_i}\tr_i\bigg)
    \end{split},
    \label{eq:hfit} 
\end{equation} where $\Pmat^l$ contains only the monomial basis of order $l$,  $\samp{\Pmat^1}$ is the stacked evaluation of this matrix at $n$ quadrature points and $\vc{c}^l_i$ are the corresponding coefficients. 
Finally, $\wt_i$ is the diagonal integration weight matrix and $\mathbbm{1}\in\real^{3n\times3}$ is a matrix of stacked $3\times3$ identity matrices -- one for each quadrature point.

>>>>

\nicetohave{now I do want that shape matching figure showing constant, linear and quadratic matching}

@@

Attempting to use $\Pmatxi$ in~\refeq{shapematch} on a per-part basis is problematic as it can become ill-posed, especially for planar boundary representations. 
To alleviate this problem we invoke the \emph{hierarchical ordering principle}, which argues that the behavior of a system is typically 
dominated by lower order effects~\cite{li2006regularities}. 
Mechanically, this principle suggests that the amount of motion modelled by increasingly high-order polynomials is, itself, decreasing. 
This implies that we can achieve acceptable shape matching results by performing shape matching hierarchically -- starting with the constant term and then 
fitting the remaining deformation with progressively higher-order expressions.

\begin{equation}
    \begin{split}
        \tr_i  & = \sum_{\prt_k \in \bar{\refX}_j} \underbrace{\mathbbm{1}^T\wt_k \samp{\Jnurbs}_k}_{B_{ik}}\vc{q}_k \\
        \vc{c}_i^1 & = \smash{\underbrace{\left(\samp{\Pmat^1}^T\wt_i\samp{\Pmat^1}\right)}_{A^1_i}}^{-1}\bigg(\underbrace{\samp{\Pmat^1}^T\wt_i\samp{\Jnurbs}_i}_{B^1_i}\vc{q}_i-\underbrace{\samp{\Pmat^1}^T\wt_i\mathbbm{1}}_{T^1_i}\tr_i\bigg)\\
        \vc{c}_i^2 & = \smash{\underbrace{\left(\samp{\Pmat^2}^T\wt_i\samp{\Pmat^2}\right)}_{A^2_i}}^{-1}\bigg(\underbrace{\samp{\Pmat^2}^T\wt_i\samp{\Jnurbs}_i}_{B^2_i}\vc{q}_i-\underbrace{\samp{\Pmat^2}^T\wt_i\samp{\Pmat^1}}_{D^2_i}\vc{c}_i^1 - \underbrace{\samp{\Pmat^2}^T\wt_i\mathbbm{1}}_{T^2_i}\tr_i\bigg)
    \end{split},
    \label{eq:hfit} 
\end{equation} where $\Pmat^l$ contains only the monomial basis of order $l$,  $\samp{\Pmat^l}$ is the stacked evaluation of this matrix at the $s$ quadrature points and $\vc{c}^l_i$ are the corresponding coefficients. 
Finally, $\wt_i$ is the diagonal integration weight matrix and $\mathbbm{1}\in\real^{3s\times3}$ is a matrix of stacked $3\times3$ identity matrices -- one for each quadrature point.

@@
